MSB205 - Boligmarkedsøkonomi og anvendt spatial økonometri

### 2021-11-08 MSB205_King_County_Silje_Sofie_Karl-Gunnnar.Rmd
Oppdatering

```{r setup, echo=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(sf)
library(here)
library(tmap)
library(sp)
library(spdep)
library(spatialreg)
library(lmtest)
library(sandwich)
library(units)
library(car)
library(foreign)
options(scipen = 999)
```

@@

# House Sales in King County, WA

@@

>>>>

```{r setup, echo=FALSE, message=FALSE}
library(tidyverse)
library(dplyr)
library(huxtable)
library(lubridate)
library(sf)
library(here)
library(tmap)
library(sp)
library(spdep)
library(spatialreg)
library(lmtest)
library(sandwich)
library(units)
library(car)
library(foreign)
library(readr)
options(scipen = 999)
```

@@

# 1. Review of papers

@@

# 2. House Sales in King County, WA

```{r}
kc_house_data <- read_csv("data/kc_house_data.csv")
attach(kc_house_data)
```

```{r}
kc_house_data <- arrange(kc_house_data, desc(date))
```

```{r}
kc_house_data <- kc_house_data %>%
    distinct(id, .keep_all = TRUE)
```

```{r}
kc_house_data_sf <- st_as_sf(kc_house_data,
             coords = c(x = "long", y = "lat"),
             crs = 4326) %>% 
    st_transform(2926)
```

Koordinater Seattle: 47.60621, -122.33207

```{r}
cbd <- st_sfc(st_point(c(-122.33207, 47.60621)), crs = 4326) %>% 
    st_transform(2926)
cbd
```

```{r}
kc_house_data_sf <-  kc_house_data_sf %>% 
  mutate(
    dist_cbd = st_distance(cbd, ., by_element = TRUE),
    dist_cbd_km = set_units(dist_cbd, km)
  )
```

# 3. Family income

```{r}
asc_b19101_fam_inc <- read.dbf("maps/censusSHP/acs_b19101_familyincome.dbf")
```
